---
title: "A basic analysis pipeline for FARS data"
author: "Lan Shui"
date: "2023-12-09" # "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{mycoursera}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignette highlights some example workflows for performing analysis for Fatality Analysis Reporting System (FARS) data, including reading data, summarizing, and visualizing accident information, using the `mycoursera` R package. 

## Load Packages
Once installed, **`mycoursera`** can be simply loaded (along with the required packages) as follows:
```{r setup,eval=FALSE}
# Load the mycoursera package
install.packages('mycoursera')
library(mycoursera)

# Load other essential packages for this tutorial
library(devtools)
library(dplyr)
library(readr)
library(maps)
library(tidyr)
library(graphics)
```

## Basic Usage
### Read data from a CSV file and returns it as a tibble
```{r,eval=FALSE}
fars_data <- fars_read("path/to/your/file.csv")
```

### Generate a filename for FARS (Fatality Analysis Reporting System) data for a given year
```{r,eval=FALSE}
filename <- make_filename(2013)
# Output: "accident_2013.csv.bz2"
```

### Read FARS data for multiple years and returns a list of tibbles
```{r,eval=FALSE}
# Read FARS data for the years 2013 and 2014
data_list <- fars_read_years(c(2013, 2014))
```

### Summarize FARS data for multiple years by counting the number of accidents
```{r,eval=FALSE}
# Summarize FARS data for the years 2013 and 2014
summary_data <- fars_summarize_years(c(2013, 2014))
```

### Maps FAR data for a specific state and year
```{r,eval=FALSE}
# Map FARS data for state number 5 in the year 2013
fars_map_state(5, 2013)
```
